Adopting agile in the large: motivations, success factors and challenges

### 2014-01-09 journal/article.tex
Research method

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

A keyword search in online databases was chosen as the search strategy. The
databases included in the search are listed in Table \ref{table:databases}. All
databases supported use of complex boolean logic in searches which allowed us
flexibility when constructing the search strings.

@@

The primary documents were coded using the Atlas TI qualitative data analysis software.
An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. The coding was also designed to have a contextual
part and a findings part as suggested by Cruzes and Dybå \cite{Cruzes2011a}. A
list of codes was established for contextual information, as presented in Table
\ref{table:contextualcodes}. Codes related to the research questions were chosen
to be created by an inductive process. The reason for inducting codes rather
than using an a priori approach was to avoid the researchers' previous
assumptions of the research area to affect the choice of codes. To give
direction for code induction seven different code families were established (see
Table \ref{table:codefamilies}). A description defining scope and examples for
codes were defined for each family. The example codes would not necessarily be
used as actual codes, and would not represent the entire or final scope of the
families.

@@

@@

\begin{table}[h]
    \begin{tabular}{ l r r r }
        \toprule
        Document    &  Matching themes  &  Total themes  &  Quotation overlap (0-3) \\
        \midrule
        P1          &  14  &  19   &  2.1  \\
        P2          &   6  &  11   &  2.4  \\
        P3          &   7  &  11   &  2.1  \\
        P4          &   2  &   4   &  2.3  \\
        P5          &  12  &  16   &  2.0  \\
        \bottomrule
    \end{tabular}
    \caption{Result of independent coding experiment}
    \label{table:codingexperiment}
\end{table}

>>>>

The study selection process inlcuded three steps, each step refining the set of
selected papers. First a database search was used to gather an initial set of
papers. This set was then refined by filtering out abstracts and finally full
text filtering. The study selection process is outlined in Figure
\ref{fig:selectionprocess}.

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

A keyword search in online databases was chosen as the means to find potential
primary studies. The databases included in the search are listed in Table
\ref{table:databases}. All databases supported use of complex boolean logic in
searches which allowed us flexibility when constructing the search strings.

@@

The primary documents were coded using the Atlas TI qualitative data analysis software.
An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. The coding was designed to have a contextual part
and a findings part as also suggested by Cruzes and Dybå \cite{Cruzes2011a}. A
list of codes was established for contextual information, as presented in Table
\ref{table:contextualcodes}. Codes related to the research questions were chosen
to be created by an inductive process. The reason for inducting codes rather
than using an a priori approach was to avoid the researchers' previous
assumptions of the research area to affect the choice of codes

@@

To give direction for code induction seven different code families were
established, as presented in Table \ref{table:codefamilies}. A description
defining scope and examples for codes were defined for each family. The example
codes would not necessarily be used as actual codes, and would not represent the
entire or final scope of the families.

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Document    &  Matching themes  &  Total themes  &  Quotation overlap (0-3) \\
        \midrule
        P1          &  14  &  19   &  2.1  \\
        P2          &   6  &  11   &  2.4  \\
        P3          &   7  &  11   &  2.1  \\
        P4          &   2  &   4   &  2.3  \\
        P5          &  12  &  16   &  2.0  \\
        \bottomrule
    \end{tabular}
    \caption{Result of independent coding experiment}
    \label{table:codingexperiment}
\end{table}
